experiment 1

### 2021-07-22 experiments/experiment 1/experiment-1.Rmd
update experiment 1

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474
CB_h_div <- -0.08
SB_gmax_div <- 0.015789474
SB_h_div <- -0.323
PB_gmax_div <- 0.015789474
PB_h_div <- -0.323

@@

```{r}
display_diversity(400)
```

@@

## Setup

@@

## Run stable state finding

@@

```{r eval = FALSE}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))

@@

## Process the stable state data

```{r}
## find various combintions of diversity
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS"))

@@

## various graphs

@@

p1  <- plot_ss_result1(var_expt,
                result_index = no_diversity,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
```

@@

```{r}
p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay2
```

```{r}
p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay3
```

## Calculate stability measures

```{r eval = FALSE}
stab_data <- var_expt %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data <- unnest(stab_data, cols = c(stability_measures))
#saveRDS(stab_data, here("experiments/experiment 1/data/stab_data.RDS"))
```

## Process and visualise stability measures

```{r}
stab_data <- readRDS(here("experiments/experiment 1/data/stab_data.RDS"))

@@

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min,
             ymax = hyst_max,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") + 
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

@@

>>>>

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474 * 0
CB_h_div <- -0.08 * 0
SB_gmax_div <- 0.015789474 * 5
SB_h_div <- -0.323  * 5
PB_gmax_div <- 0.015789474  * 5
PB_h_div <- -0.323  * 5

@@

```{r}
display_diversity(20)
```

@@

## Finding

@@

Run stable state finding

@@

```{r eval = FALSE}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))

@@

Process the stable state data

Bring in various stable state datasets
```{r eval = FALSE}
## sim length 80'000, 20 x 20 factorial, reference maximum diversity
var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
  mutate(sim_length = 80000)
stab_data1 <- var_expt1 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data1 <- unnest(stab_data1, cols = c(stability_measures))
saveRDS(stab_data1, here("experiments/experiment 1/data/stab_data_80000.RDS"))

## sim length 1'000'000, 20 x 20 factorial, reference maximum diversity
var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
  mutate(sim_length = 1000000)
stab_data2 <- var_expt2 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data2 <- unnest(stab_data2, cols = c(stability_measures))
saveRDS(stab_data2, here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 5x maximum diversity
var_expt3 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
  mutate(sim_length = 1000000)
stab_data3 <- var_expt3 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data3 <- unnest(stab_data3, cols = c(stability_measures))
saveRDS(stab_data3, here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

## sim length 300'000, 20 SBPBgrad, reference maximum diversity
var_expt4 <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
  mutate(sim_length = 300000)
stab_data4 <- var_expt4 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data4 <- unnest(stab_data4, cols = c(stability_measures))
saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))

## SS, no diversity, all diversity, CB only, and SBPB only

```{r}
## find various combinations of diversity
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))

@@

@@

p1  <- plot_ss_result1(var_expt,
                result_index = no_diversity,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

#junk1 <- var_expt[no_diversity,]$ss_res[[1]]
```

@@

```{r}
p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay2

#ss_result1 <- var_expt[no_diversity,]$ss_res[[1]]
#ss_result2 <- var_expt[max_only_CB_diversity,]$ss_res[[1]]

```{r}
p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay3

#ss_result3 <- var_expt[max_only_SBPB_diversity,]$ss_res[[1]]

## Look at stability measures

```{r}
stab_data1 <- readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
stab_data2 <- readRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
stab_data <- bind_rows(stab_data1, stab_data2)

@@

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min,
             ymax = hyst_max,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") + 
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 8e4) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min,
             ymax = hyst_max,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") + 
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

@@

## Extra SBPB diversity

```{r}
var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

p1  <- plot_ss_result1(var_expt_x,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

p1  <- plot_ss_result1(var_expt_x,
                result_index = 19,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

p_overlay1 <- plot_ss_result2(var_expt_x[1,]$ss_res[[1]],
                             var_expt_x[19,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1

stab_data_x %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s, y = hyst_range)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

stab_data_x %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s,
             ymin = hyst_min,
             ymax = hyst_max)) +
  geom_ribbon(alpha = 0.5) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

## What effect of changing the length of the simulations

```{r}
var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS"))

p1_short  <- plot_ss_result1(var_expt2,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1_short

p1_long  <- plot_ss_result1(var_expt1,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1_long
